Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-07 paper.tex
Figure 3 and 4 on same page
Figure placement rework

@@

\begin{figure*}
  \centering
  \begin{subfigure}{.475\textwidth}
    \includegraphics[width=8cm]{method-a.pdf}\\
    \subcaption{Spatial aggregation based on provincial administrative boundaries}
    \label{fig:method-a}
  \end{subfigure}%
  \begin{subfigure}{.475\textwidth}
    \includegraphics[width=8cm]{method-b.pdf}\\
    \subcaption{\todo{Alvin: caption to explain what this is}}
    \label{fig:method-b}
  \end{subfigure}%
  \hfill%
  \begin{subfigure}{0.9\textwidth}
    \includegraphics[width=15cm]{method-c.pdf}\\
    \subcaption{Yet another subfigure \todo{Alvin: caption to explain what this is}}
    \label{fig:method-c}
  \end{subfigure}%
  \caption{General caption of the image \todo{Alvin: caption to explain what this is}}
  \label{fig:method}
\end{figure*}

@@

\subsection{Time based analysis}

\begin{figure}
\centering
\includegraphics[width=8.6cm]{avg-all}
\caption{Distribution of iRail route planning API queries on average per day of the week between October 2012 and December 2015}
\label{fig:average}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8.6cm]{dec24}
\caption{Comparison of route planning queries on December 24th (Christmass Eve) 2015 with the average on a Thursday between October 2012 and December 2015. The illustration shows that people started going home earlier than usual.}
\label{fig:dec24}
\end{figure}

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=14cm]{method-c.pdf}\\
  \caption{Yet another figure \todo{Alvin: caption to explain what this is}}
  \label{fig:method-c}
\end{figure*}

@@

\begin{figure}[h]
  \centering
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-a.pdf}\\
    \subcaption{Lines and dots\todo{Alvin}} % 4 words max
    \label{fig:method-a}
  \end{subfigure}%
  \begin{subfigure}{.2375\textwidth}
    \includegraphics[width=4cm]{method-b.pdf}\\
    \subcaption{arrows and dots\todo{Alvin}} % 4words max
    \label{fig:method-b}
  \end{subfigure}%
  \vspace{5.0pt}% To create a bit of vertical space between the 2 figure captions
  \caption{With the arrow and dots and the lines and dots you can see that TODO \todo{Alvin: can you write a caption here?}}
\end{figure}

@@

\subsection{Time based analysis}
\begin{figure}[h]
\centering
\includegraphics[width=8.6cm]{avg-all}
\caption{Distribution of iRail route planning API queries on average per day of the week between October 2012 and December 2015}
\label{fig:average}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=8.6cm]{dec24}
\caption{Comparison of route planning queries on December 24th (Christmass Eve) 2015 with the average on a Thursday between October 2012 and December 2015. The illustration shows that people started going home earlier than usual.}
\label{fig:dec24}
\end{figure}

@@
